a and generators

### 2022-05-03 documentos/generators.tex
Too tired to write descriptive message
arrrggghhhhh fixed!

\pgfmathsetmacro{\unitstep}{1.5}

@@

\node at (-0.6,0.5) {(b)} ;

@@

\node at (-0.6,0.5) {(c)} ;

@@

\node at (-0.6,0.5) {(d)} ;

@@

\node at (-0.6,0.5) {(e)} ;

@@

\includegraphics[width=\columnwidth]{oneQ_PCEGs-crop}
\caption{Connection between rows and columns of $a$ and single qubit PCE generators.
The rows or columns of $a$ and the diagrams of the generators are either 
symmetric or anti-symmetric under reflection.
\cpnote{Mejorar figura, poner matriz de tamano normal, poner loslabels de los generadores, mejorrar el caption, cambiar los cuadrios.}

>>>>

\node at (-2.5,-0.9) {
$
\begin{pmatrix}
1 & 1 & 1 & 1\\
1 & 1 & -1 & -1\\
1 & -1 & 1 & -1\\
1 & -1 & -1 & 1
\end{pmatrix}
\longleftrightarrow
% \mcG_1
$
} ;
\pgfmathsetmacro{\unitstep}{1.2}

@@

\node at (0.5,-3.5) {$\mcG_0$} ;
% \node at (-0.6,0.5) {(b)} ;

@@

\node at (0.5,-3.5) {$\mcG_1$} ;

@@

\node at (0.5,-3.5) {$\mcG_2$} ;
% \node at (-0.6,0.5) {(d)} ;

@@

\node at (0.5,-3.5) {$\mcG_3$} ;
% \node at (-0.6,0.5) {(e)} ;

@@

% \includegraphics[width=\columnwidth]{oneQ_PCEGs-crop}
\caption{Connection between rows and columns of $a$ and single qubit PCE
generators. We also include the corresponding 
labels $\mcG_\alpha$ of the generators.
% The rows or columns of $a$ and the diagrams of the generators are either 
% symmetric or anti-symmetric under reflection.
% \cpnote{Mejorar figura, poner matriz de tamano normal, poner loslabels de los generadores, mejorrar el caption, cambiar los cuadrios.}
